Figures and Analysis for 2023 Manuscript

### 2023-10-20 data-raw/Manuscript2023_Workflow.Rmd
Added label expressions 10^ and 2^ for plots on poster.

pl_7A <- my_preds %>%
  group_by(Chemical,
           Species,
           Route, Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc_trans)) != n(),
         # model %in% c("model_flat"),
         exclude %in% FALSE,
         Detect %in% TRUE) %>%
  mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc_trans / meanConc,
         foldPred = Conc_est / Conc_trans) %>% 
  # For percentages
  # ungroup() %>%
  # filter(model %in% c("model_flat")) %>%
  # count((foldPred >= 0.5 & foldPred <= 2) & !(foldConc >= 0.5 & foldConc <= 2)) %>%
  # {100*.[[2,2]]/(.[[1,2]] + .[[2,2]])}
  # For Plotting
  ggplot(aes(
    y = foldPred,
    x = foldConc
  )) +
  geom_bin2d(bins = 40, color = NA) +
  geom_hline(yintercept = c(0.5, 2), linetype = "dashed") +
  geom_vline(xintercept = c(0.5, 2), linetype = "dashed") +
  facet_grid(cols = vars(model)) +
  scale_x_log10(limits = c(0.0001, 100)) +
  scale_y_log10(limits = c(0.001, 1000)) +
  scale_fill_viridis_c(option = "cividis",
                       limits = c(1, 100),
                       oob = oob_squish) +
  labs(y = "Model Error",
       x = "Data Variability") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "ModelPerformance_vDataVariability_2023-10-02.png"),
       height = 3,
       width = 6.5,
       device = "png",
       dpi = 300,
       units = "in")

@@

lombard_abbr <- lombard_abbr %>%
  mutate(Species = "human", model = "lombardo") %>%
  rename(Vss = hVss, CLtot = hCltot) %>%
  mutate(CLtot = CLtot*60/1000) %>% # Lombardo reports this as mL/min/kg, need L/h/kg
  filter(DTXSID %in% comparable_ids)

@@

sfig4A <- lombardo_hist %>% ggplot(aes(x = log2(Vss), color = Source,
                             group = Source)) +
  geom_freqpoly(aes(y = after_stat(ndensity)),
                linewidth = 2/.pt,
                bins = 20) +
  labs(y = "Scaled Frequency") +
  scale_color_manual(values = c("black", "#1064c9")) +
  guides(color = guide_legend(nrow = 2, linewidth = 1)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold", size = 12),
        text = element_text(size = 10),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text = element_text(face = "bold"),
        legend.position = "bottom",
        legend.key = element_blank(),
        legend.title = element_text(face = "bold"),
        legend.text = element_text())

other_meta <- read_csv(
  file = paste0(Sys.getenv("FIG_DIR"), "SupTableInVivoDatandPreds.csv")) %>%
  dplyr::select(DTXSID, fbioh, fbior) %>%
  filter(DTXSID %in% my_tkstats$Chemical)

sfig4B <- other_meta %>% left_join(my_tkstats, by = c("DTXSID" = "Chemical")) %>%
  filter(Species %in% c("rat")) %>%
  filter(!is.na(Fgutabs.tkstats),
         !is.na(fbior)) %>%
  distinct(DTXSID, Species,
           Fgutabs.tkstats, fbior) %>%
  pivot_longer(cols = c(Fgutabs.tkstats, fbior),
               names_to = "Source",
               values_to = "Fgutabs") %>%
    mutate(Source = ifelse(str_detect(Source, "tkstats"), "invivoPKfit",
                           "Caco-2 Paper")) %>%
    ggplot(mapping = aes(
      x = Fgutabs,
      y = reorder(DTXSID, Fgutabs)
    )) +
    geom_point(aes(color = Source),
               shape = 24,
               position = position_dodge(0.7),
               size = 5/.pt, stroke = 2.5/.pt) +
    scale_color_manual(values = c("black", "green4"),
                       breaks = c("invivoPKfit", "Caco-2 Paper")) +
  guides(color = guide_legend(nrow = 2)) +
    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
          panel.background = element_blank(),
          panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(face = "bold", size = 12),
          text = element_text(size = 10),
          axis.ticks = element_blank(),
          axis.line = element_blank(),
          axis.text = element_text(face = "bold"),
          axis.title.y = element_blank(),
          legend.position = "bottom",
          legend.key = element_blank(),
          legend.title = element_text(face = "bold"),
          legend.text = element_text())

>>>>

pl_7A <- my_preds %>%
  group_by(Chemical,
           Species,
           Route, Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc_trans)) != n(),
         # model %in% c("model_flat"),
         exclude %in% FALSE,
         Detect %in% TRUE) %>%
  mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc_trans / meanConc,
         foldPred = Conc_est / Conc_trans) %>%
  # For percentages
  # ungroup() %>%
  # filter(model %in% c("model_flat")) %>%
  # count((foldPred >= 0.5 & foldPred <= 2) & !(foldConc >= 0.5 & foldConc <= 2)) %>%
  # {100*.[[2,2]]/(.[[1,2]] + .[[2,2]])}
  # For Plotting
  ggplot(aes(
    y = foldPred,
    x = foldConc
  )) +
  geom_bin2d(bins = 40, color = NA) +
  geom_hline(yintercept = c(0.5, 2), linetype = "dashed") +
  geom_vline(xintercept = c(0.5, 2), linetype = "dashed") +
  facet_grid(cols = vars(model)) +
  scale_x_log10(labels = scales::label_math(format = log10),
                limits = c(0.001, 100)) +
  scale_y_log10(labels = scales::label_math(format = log10),
                limits = c(0.001, 1000)) +
  scale_fill_viridis_c(option = "cividis",
                       limits = c(1, 100),
                       oob = scales::oob_squish) +
  labs(y = "Model Error",
       x = "Data Variability") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

pl_7A
ggsave(paste0(Sys.getenv("FIG_DIR"),
              "ModelPerformance_vDataVariability_2023-10-19.png"),
       height = 3,
       width = 6.5,
       device = "png",
       dpi = 300,
       units = "in")

@@

lombard_abbr <- lombard_abbr %>%
  mutate(Species = "human", model = "Lombardo et al.") %>%
  rename(Vss = hVss, CLtot = hCltot) %>%
  mutate(CLtot = CLtot*60/1000) %>% # Lombardo reports this as mL/min/kg, need L/h/kg
  filter(DTXSID %in% comparable_ids)

@@

sfig4A <- lombardo_hist %>% 
  ggplot(aes(x = log2(Vss), color = Source,
             group = Source)) +
  geom_freqpoly(aes(y = after_stat(ndensity)),
                linewidth = 2/.pt,
                bins = 20) +
  labs(y = "Scaled Frequency",
       x = "Vss") +
  scale_x_continuous(labels = scales::label_math(expr = 2^.x)) +
  scale_color_manual(values = c("black", "#1064c9")) +
  guides(color = guide_legend(nrow = 2, linewidth = 1)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold", size = 12),
        text = element_text(size = 10),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text = element_text(face = "bold"),
        legend.position = "bottom",
        legend.key = element_blank(),
        legend.title = element_text(face = "bold"),
        legend.text = element_text())

sfig4A
other_meta <- read_csv(
  file = paste0(Sys.getenv("FIG_DIR"), "SupTableInVivoDatandPreds.csv")) %>%
  dplyr::select(DTXSID, fbioh, fbior) %>%
  filter(DTXSID %in% my_tkstats$Chemical)

sfig4B <- other_meta %>% left_join(my_tkstats, by = c("DTXSID" = "Chemical")) %>%
  filter(Species %in% c("rat")) %>%
  filter(!is.na(Fgutabs.tkstats),
         !is.na(fbior)) %>%
  distinct(DTXSID, Species,
           Fgutabs.tkstats, fbior) %>%
  pivot_longer(cols = c(Fgutabs.tkstats, fbior),
               names_to = "Source",
               values_to = "Fgutabs") %>%
    mutate(Source = ifelse(str_detect(Source, "tkstats"), "invivoPKfit",
                           "Honda et al.")) %>%
    ggplot(mapping = aes(
      x = Fgutabs,
      y = reorder(DTXSID, Fgutabs)
    )) +
    geom_point(aes(color = Source),
               shape = 24,
               position = position_dodge(0.7),
               size = 5/.pt, stroke = 2.5/.pt) +
    scale_color_manual(values = c("black", "green4"),
                       breaks = c("invivoPKfit", "Honda et al.")) +
  labs(x = "Oral Bioavailability") +
  guides(color = guide_legend(nrow = 2)) +
    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
          panel.background = element_blank(),
          panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(face = "bold", size = 12),
          text = element_text(size = 10),
          axis.ticks = element_blank(),
          axis.line = element_blank(),
          axis.text = element_text(face = "bold"),
          axis.title.y = element_blank(),
          legend.position = "bottom",
          legend.key = element_blank(),
          legend.title = element_text(face = "bold"),
          legend.text = element_text())
